A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-26 0_main.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

Based on a skeletonization of the 2D outline shape of a single layer we generate a 3D surface mesh, the union of cones.
By slicing the surface at regular heights we obtain contour parallel toolpaths which cover the 2D area of a single layer.
The heights of the 3D mesh are first altered:
the heights at central ridges in the 3D surface are flattened to be parallel with the slicing planes in order to prevent over- and underfill
and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.

>>>>

Based on a skeletonization of the 2D outline shape of a single layer we generate a 3D surface mesh, the union of cones.
By slicing the surface at regular heights we obtain contour parallel toolpaths which cover the 2D area of a single layer.
The heights of the 3D mesh are first altered:
the heights at central ridges in the 3D surface are quantized in order to prevent over- and underfill
and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.

### 2019-08-26 4_method.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

Our framework can be thought of as following these steps:
\begin{itemize}
\item Compute the skeleton of the input shape
\item Assign each node a height in terms of bead count based on the local feature size
\item Identify central regions of the UoC
\item Flatten the central regions at heights equal to the nearest integer bead count
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Flattened}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and flatten those regions to heights of the nearest integer \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Flattening the central mesh regions and smoothing are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we flatten those regions to integer heights.
More specifically we round the heights to integer bead count values.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framework the function $b$ is determined by a beading strategy.

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Flattening}
For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

>>>>

Our framework can be thought of as following these steps:
\begin{itemize}
\item Compute the skeleton of the input shape
\item Assign each node a height in terms of bead count based on the local feature size
\item Identify central regions of the UoC
\item Quantize the height of central ridges and peaks
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Quantized}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and quantize the height in those regions \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
More specifically we round the heights to integer bead count values.
Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values coincides with a slicing height.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a quantization operator which maps a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framework the function $q$ is determined by a beading strategy.

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Quantization}
For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $q^{-1}(n) := \argmax_d q(d) = n$, which gives the feature diameter at which $q$ jumps from $n$ to $n+1$ beads.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

### 2019-08-26 5_generalization.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

\begin{definition}\label{beading_strategy_definition}
We define a beading strategy as the following set:
$$
\left\{ \alpha_\text{max}, f(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$f(d)$ (flattening operator),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ f^{-1}(n + 1) - f^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
\end{enumerate}

@@

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( f^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
f(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
f(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $f^-(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
f(d) &= f^-(d) +
\begin{cases}
-1 & \text{ if } f^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  f^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_\text{pref} \\
W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

>>>>

\begin{definition}\label{beading_strategy_definition}
We define a beading strategy as the following set:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$q(d)$ (quantization operator),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
\end{enumerate}

@@

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
t(n) &= 0 \\
q(d) &=
\begin{cases}
1 & \text{ if } d < w_\text{pref} \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w_\text{pref} & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w_\text{pref} / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}

@@

\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
q(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $q^-(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
q(d) &= q^-(d) +
\begin{cases}
-1 & \text{ if } q^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  q^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

@@

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}

@@

\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
E(n,d) &= d - n w_\text{pref} \\
W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}
